Manuscript

### 2024-05-30 Manuscript.qmd
changed stats

P_individual <- P_all+ylim(0,0.8)+
  facet_wrap(~sampleID,ncol=3)+#ylim(0.15,NA)+
  ggpubr::stat_regline_equation(label.x = 0.5, label.y = 0.65,
    aes(label =  paste(after_stat(eq.label), after_stat(adj.rr.label,p.value), sep = "~~~~")),show.legend = FALSE,
    formula = y~x
  )+
  theme(
    strip.background = element_rect(fill = "white", colour = NA),
    strip.text = element_text(colour = "black"),
    panel.border = element_rect(colour="black")
  )

>>>>

P_individual <- P_all+ylim(0,0.8)+
  facet_wrap(~sampleID,ncol=3)+#ylim(0.15,NA)+
  ggpubr::stat_regline_equation(label.x = 0.5, label.y = 0.65,
    aes(label =  paste(after_stat(eq.label), after_stat(adj.rr.label), sep = "~~~~")),show.legend = FALSE,
    formula = y~x
  )+
  theme(
    strip.background = element_rect(fill = "white", colour = NA),
    strip.text = element_text(colour = "black"),
    panel.border = element_rect(colour="black")
  )
